---
title: "help_with_ZYXU_package"
author: "ZY_XU"
date: "11/27/2018"
output:
  pdf_document: default
  html_document: default
---


#   How to play with "ZYXUnaivelasso" ?
#####   This is a package that calculate the lasso problem(very, very, very naive),
##### since I set the lambda to a fixed value 2, the result in example is not
##### different with normal linear regression(kind of embarrassing), but I still
##### want to write it out, just for fun!

##### Hope you guys have fun here ! :)

## How to library it?
 ** First, you need to download the .tar file named "ZYXUnaivelasso_1.0.tar", then run 
the code below:**


```{r}
rm(list=ls())
if (!require("ZYXUnaivelasso")) {
  install.packages("ZYXUnaivelasso_1.0.tar.gz", 
                 repos = NULL, 
                 type = "source") # do this once per lifetime
  stopifnot(require("ZYXUnaivelasso")) # do this once per session
}




```

**You can Shutdown R studio and open "help.R" **
```{r}
require("ZYXUnaivelasso")

```

## How to use it?
 ** you can use lasso function to calculate the problem with your own data, 
same as the lm() function in simple linear regression with only two parameter
beta0 and beta1.**

#### There are four function,
#### 1:the "lasso" you use to fit model. 2: The "print" you use to print coefficients
#### 3:The "coef" you use to extract coefficients
#### 4:The predict you use to predict new values


```{r }
example(lasso)
?lasso
?coef.las
?predict.las
?print.las
?area
```

**I wirte all the help web by myself, whether there is link you can click into it to see the description I wrote about my package~~**
